\begin{thebibliography}{30}
 
\bibitem{612}{ Amini, Mohammad and Abukari, Arnold. (2020). "ERP Systems Architecture For The Modern Age: A Review of The State of The Art Technologies." 
            Journal of Applied Intelligent Systems and Information Sciences. Volume 1(2), pp.70-90. 
            Available: https://doi.org/10.22034/jaisis.2020.232506.1009.
    %         [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1lZj0R8UVPVGuOzbX13NyD6v4GVDhq02v/view?usp=share_link}{Link GoogleDrive}
    %  }]
}

\bibitem{D94}{
    Bender, B.; Bertheau, C. and Gronau, N. (2021). "Future ERP Systems: A Research Agenda." In Proceedings of the 23rd International Conference on Enterprise Information Systems. 2, pp.776-783.
    Available: http://dx.doi.org/10.5220/0010477307760783.
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1iKgZTgkftoMcxT-wDkd-sMS3bs7aCszw/view?usp=share_link}{Link GoogleDrive}
    %  }]
} 

\bibitem{6C1}{
    Chaitanya K. Rudrabhatla. (2020). "Impacts of Decomposition Techniques on Performance and Latency of Microservices." International Journal of Advanced Computer Science and Applications(IJACSA). 11(8).
    Available: http://dx.doi.org/10.14569/IJACSA.2020.0110803.
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1e_opNADm8CpCWBATgAc36tKWlp_lzeoz/view?usp=share_link}{Link GoogleDrive}
    %  }]
}

\bibitem{5FA}{
    Slamaa, A.A., El-Ghareeb, H.A. , Saleh, A.A. (2021). "A Roadmap for Migration System-Architecture Decision by Neutrosophic-ANP and Benchmark for Enterprise Resource Planning Systems." IEEE Access . 9, pp.48583-48604.
    Available: https://doi.org/10.1109/ACCESS.2021.3068837.
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1TX9qX9CrP4_XbTsv4Gvad5cZqAnTM5Zj/view?usp=share_link}{Link GoogleDrive}
    %  }]
} 

\bibitem{74C}{
    Sam Newman, \textit{Monolith to Microservices}, Sebastopol, CA: O’Reilly Media, Inc., 2020, pp. 12-15
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1JJWrGXzsbE9ZIpWqbFBJlPEj_QzxdVWa/view?usp=share_link}{Link GoogleDrive}
    %  }]
}

\bibitem{0BD}{
    Dragoni, N., Giallorenzo, S., Lafuente, A. L., Mazzara, M., Montesi, F., Mustafin, R. Safina, L. (2017). "Microservices: Yesterday, Today, and Tomorrow". Present and Ulterior Software Engineering, 195-216. 
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1DSuVusC9lInJipC4jNDVhBwVLOi0nIYN/view?usp=share_link}{Link GoogleDrive}
    %  }]
}


\bibitem{1C7}{
    Richardson, C. (2018) Microservice patterns: With examples in Java. Shelter Island, NY: Manning Publications. 
}
\bibitem{208}{
    Cruz, D.D., Henriques, P.R. and Pinto, J.S. (2009) Code analysis: past and present [Preprint]. Available at: https://hdl.handle.net/1822/14352. 
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1YiTn-C_ABVdWR6HI8Dnd04GD-1NS-fXj/view?usp=share_link}{Link GoogleDrive}
    %  }]
}
\bibitem{2C9}{
    Jain, A.K. and Dubes, R.C. (1988) Algorithms for clustering data. Englewood Cliffs, NJ: Prentice Hall. 
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1mHbYJWWamfJutZb4O16AZ-uBvqWtW1o_/view?usp=share_link}{Link GoogleDrive}
    %  }]
}


\bibitem{ECD}{ 
    Khaled Sellami, Mohamed Aymen Saied, and Ali Ouni. (2022). "A Hierarchical
    DBSCAN Method for Extracting Microservices from Monolithic Applications" In The International Conference on Evaluation and Assessment in Software Engineering 2022 (EASE 2022). ACM, New York, NY, USA, 11.
    Available: https://doi.org/10.1145/3530019.3530040. 
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1KFyAtmbiGjZv-EPHJEmNtCkujt0eJyqy/view?usp=share_link}{Link GoogleDrive}
    %  }]
}

\bibitem{8EA}{
    A. K. Kalia, J. Xiao, R. Krishna, S. Sinha, M. Vukovic, and D. Banerjee, “Mono2micro: A practical and effective tool for decomposing monolithic Java applications to microservices,” Proceedings of the 29th ACM Joint Meeting on European Software Engineering Conference and Symposium on the Foundations of Software Engineering, 2021. 
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1WmF6ZeCrqqnPQdkCPnC6_xdnPGG1KZl4/view?usp=share_link}{Link GoogleDrive}
    %  }]
}

\bibitem{5B1}{
    A. Selmadji, A.-D. Seriai, H. L. Bouziane, R. Oumarou Mahamane, P. Zaragoza, and C. Dony, “From monolithic architecture style to Microservice one based on a semi-automatic approach,” 2020 IEEE International Conference on Software Architecture (ICSA), 2020.
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1c8ueFaAudCHxgW-aY3sXu09FE2SrJIvM/view?usp=share_link}{Link GoogleDrive}
    %  }]
}

 \bibitem{3D3}{
    M. Fokaefs, N. Tsantalis, A. Chatzigeorgiou, and J. Sander, “Decomposing object-oriented class modules using an agglomerative clustering technique,” 2009 IEEE International Conference on Software Maintenance, 2009. 
    % [\textcolor{blue}{
    %     \href{https://drive.google.com/file/d/1XFM8w0rJBwdnaGLUiPL5jH2TinoszqrR/view?usp=share_link}{Link GoogleDrive}
    %  }]
}

\bibitem{odoo}{
    “Odoo documentation,” Odoo. [Online]. Available: https://www.odoo.com/documentation/16.0/. [Accessed: 21-Mar-2023]. 
}

\bibitem{docker}{
    “Docker docs,” Docker. [Online]. Available: https://docs.docker.com/. [Accessed: 21-Mar-2023]. 
}

\bibitem{kong}{
    “Kong documentation,” Kong. [Online]. Available: https://docs.konghq.com/. [Accessed: 21-Mar-2023]. 
}

\bibitem{inspect}{
    “inspect — Inspect live object,” inspect. [Online]. Available: https://docs.python.org/3/library/inspect.html . [Accessed: 21-Mar-2023]. 
}

\bibitem{scipy}{
    “Scipy documentation,” SciPY. [Online]. Available: https://docs.scipy.org/doc/scipy/. [Accessed: 21-Mar-2023]. 
}

\bibitem{AD7}{
    V. Salis, T. Sotiropoulos, P. Louridas, D. Spinellis, and D. Mitropoulos, “PYCG: Practical \textit{call graph} generation in python,” 2021 IEEE/ACM 43rd International Conference on Software Engineering (ICSE), 2021. 
}
\bibitem{09E} {
D. Müllner, “Modern hierarchical, agglomerative clustering algorithms,” arXiv.org, 12-Sep-2011. [Online]. Available: https://arxiv.org/abs/1109.2378. }

\end{thebibliography}