\chapter*{\textit{ABSTRACT}}

\begin{longtable}{@{}p{2.5cm} l p{10.3cm}}
	\textit{Name} 			& : & Albertus Septian Angkuw \\
	\textit{Department}		& : & \textit{Informatics} \\
	\textit{Title}			& : & \textit{Application of Hierarchical Clustering Method for Microservice Decomposition from Monolith on Enterprise Resource Planning} \\
	
	
\end{longtable}


\textit{
	Enterprise Resource Planning (ERP) applications can be built using Monolith Architecture, Service-Oriented Architecture, and Microservice. The Monolith architecture is simple but lacks scalability and sustainability in development, while Microservice architecture is a modern approach suitable for vertically and horizontally scaled enterprise applications. The benefits of Microservice architecture have led companies to migrate from Monolith architecture to Microservices. However, this migration process has proven to be hard and costly, particularly in identifying the components of the Monolith application. Component identification can be semi-automated using clustering algorithms. The clustering algorithm used is Hierarchical Clustering which has linkages such as single linkage, complete linkage, and average linkage. In this research, Odoo, an ERP application, is decomposed from Monolith to Microservices by analyzing the program's code graph then  inserting the graph into Hierarchical Clustering. The results of the clustering are tested by evaluating cohesion and coupling for each linkage, followed by selecting the parts to be implemented. Based on the testing, it was found that the Average linkage is suitable for creating service clusters with good coupling and cohesion. The ideal number of services in the Average linkage ranges from 175 to 245 services. From the table structure that is formed when implementation shows Hierarchical Clustering can separate unconnected modules and identify services with strong relationships, as in case
	in the 10th partition with Module Product and Module Point of Sale and on case
	on the 17th partition with Module Calendar.}


\noindent \textit{Keywords:  Decomposition, Hierarchical Clustering, Microservice, Monolith, Enterprise Resource Planning, Odoo}